---
title: "Lab 4"
author: "Bryanna Matias"
date: "9/14/2020"
output: html_document
bibliography: references.bib
---

```{r}
library(tidyverse)
```

### Making a Graph from the Daily Reports from 3/11/2020 and 9/13/2020

```{r}
report_03_11_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-11-2020.csv")) %>%
  rename(Country_Region = "Country/Region", Province_State = "Province/State")
```
```{r}
report_09_13_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-13-2020.csv"))
```

## Exercise 1

* Part 1: Interactive Data Tables

```{r}
library(DT)
```

# March Data
```{r}
str(report_03_11_2020)
```

```{r, eval=FALSE}
View(report_03_11_2020)
```

```{r}
datatable(report_03_11_2020)
```

#September Data

```{r}
str(report_09_13_2020)
```

```{r, eval=FALSE}
View(report_09_13_2020)
```

```{r}
datatable(report_09_13_2020)
```

* Part 2: Collecting Data From Multiple Entries Representing Different Regions

```{r}
country1 <-report_03_11_2020 %>% group_by(Country_Region) %>% summarise(Deaths = sum(Deaths))
```

* Part 3: Counts of Confirmed Cases per U.S. State using filter()

```{r}
# Deaths in March
USA1 <- report_03_11_2020 %>% filter(Country_Region == "US")%>% group_by(Province_State) %>% summarise(Deaths = sum(Deaths))%>% slice(1:10)
```
```{r}
# Deaths in September
USA2 <- report_09_13_2020 %>% filter(Country_Region == "US")%>% group_by(Province_State) %>% summarise(Deaths = sum(Deaths))%>% slice(1:10)
```

```{r}
#Confirmed in March
USA3 <- report_03_11_2020 %>% filter(Country_Region == "US")%>% group_by(Province_State) %>% summarise(Confirm = sum(Confirmed))%>% slice(1:10)
```
```{r}
#Confirmed in September
USA4 <- report_09_13_2020 %>% filter(Country_Region == "US")%>% group_by(Province_State) %>% summarise(Confirm = sum(Confirmed))%>% slice(1:10)
```

* Part 4: Data of Only Top 10 Countries using arrange_by() and slide()

```{r}
Deaths <- country1 %>% arrange(desc(Deaths)) %>% slice(1:10)
```
```{r}
country2 <- report_03_11_2020 %>% group_by(Country_Region) %>% summarise(Confirm = sum(Confirmed))
```
```{r}
Confirmed <- country2 %>% arrange(desc(Confirm)) %>% slice(1:10)
```

## Exercise 2

* Part 1: ggplots

```{r}
#March Data
ggplot(data = Deaths, aes(x = Country_Region, y = Deaths, color = Country_Region)) + geom_point () + theme(legend.position="none") 

#+ labs( x + "Days" , y + "Death")
```

```{r}
ggplot(data = Confirmed, aes(x = Country_Region, y = Confirm, color = Country_Region)) + geom_point () + theme(legend.position="none") 

#+ labs( x = "Days" , y + "Confirmed")
```

```{r}
country3 <- report_09_13_2020 %>% group_by(Country_Region) %>% summarise(Deaths = sum(Deaths))
```

```{r}
Deaths <- country3 %>% arrange(desc(Deaths)) %>% slice(1:10)
```

```{r}
country4 <- report_09_13_2020 %>% group_by(Country_Region) %>% summarise(Confirm = sum(Confirmed))
```
```{r}
Confirmed <- country4 %>% arrange(desc(Confirm)) %>% slice(1:10)
```

```{r}
#September Data
ggplot(data = Deaths, aes(x = Country_Region , y = Deaths , color = Country_Region)) + geom_point () + theme(legend.position = "none")
```

```{r}
ggplot(data = Confirmed, aes(x = Country_Region , y = Confirm , color = Country_Region)) + geom_point () + theme(legend.position = "none")
```

* Part 2: geom_bar

```{r}
#Deaths in March
ggplot(data = USA1, aes(x = Province_State , y = Deaths , color = Province_State)) + geom_bar(stat="identity") + theme(legend.position = "none")
```

```{r}
#Deaths in September
ggplot(data = USA2, aes(x = Province_State , y = Deaths , color = Province_State)) + geom_bar(stat="identity") + theme(legend.position = "none")
```

```{r}
#Confirmed in March
ggplot(data = USA3, aes(x = Province_State , y = Confirm , color = Province_State)) + geom_bar(stat="identity") + theme(legend.position = "none")
```

```{r}
#Confirmed in September
ggplot(data = USA4, aes(x = Province_State , y = Confirm , color = Province_State)) + geom_bar(stat="identity") + theme(legend.position = "none")
```

Application written in R [@RCoreTeam] using the Shiny framework [@Chang2015].

# References









