---
title: "Lab 6 Report"
author: "Bryanna Matias"
date: "10/7/2020"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(maps)
library(mapdata)
library(lubridate)
library(viridis)
library(wesanderson)
library(plotly)
library(RColorBrewer)
library(gganimate)
library(transformr)
```

# World Confirmed Cases: 3/26/20 V. Today

*  World confirmed cases from seven months ago (3/26/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
daily_report1 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv")) %>% 
  rename(Long = "Long_") 
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# graphing data
ggplot(daily_report1, aes(x = Long, y = Lat, size = Confirmed/1000)) +
    borders("world", colour = "grey40", fill = "thistle1") +
    theme_minimal() +
    geom_point(shape = 21, color='hot pink', fill='gold', alpha = 0.5) +
    labs(title = 'World COVID-19 Confirmed Cases (3/26/20)',x = '', y = '',
        size="Cases (x1000))") +
    theme(legend.position = "right") +
    coord_fixed(ratio=1.5)
```

* World confirmed cases today (10/06/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
daily_report2 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/10-06-2020.csv")) %>% 
  rename(Long = "Long_") 
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(daily_report2, aes(x = Long, y = Lat, size = Confirmed/1000000)) +
    borders("world", colour = "grey40", fill = "thistle1") +
    theme_minimal() +
    geom_point(shape = 21, color='hot pink', fill='gold', alpha = 0.5) +
    labs(title = 'World COVID-19 Confirmed Cases (10/06/20)',x = '', y = '',
        size="Cases (x1000000))") +
    theme(legend.position = "right") +
    coord_fixed(ratio=1.5)
```

# Visualizing the Number of Confirmed Cases in the US by State from Seven Months Ago (3/26/20) and Today (10/06/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
#Joining Tables

Confirmed_State_3_26<-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv")) %>%
  filter (Country_Region == "US") %>% 
  group_by(Province_State, Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed)) 

Confirmed_State_10_06 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/10-06-2020.csv")) %>% 
  filter (Country_Region == "US") %>% 
  group_by(Province_State, Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed)) 

Confirmed_State_10_06 <- Confirmed_State_10_06 %>% 
  filter(Province_State != "Recovered") 

Confirmed_State_3_26_10_06_joined <- full_join(
      Confirmed_State_10_06,Confirmed_State_3_26, by = c("Province_State"))

Confirmed_State_3_26_10_06_joined <- full_join(
      Confirmed_State_10_06, Confirmed_State_3_26, by = c("Province_State")) %>% 
      rename(Confirmed_3_26_2020 = "Confirmed.x", Confirmed_10_06_2020 = "Confirmed.y") %>% 
      select(-Country_Region.x, -Country_Region.y) %>% 
      replace_na(list(Confirmed_3_26_2020 = 0))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# which(is.na(Confirmed_State_3_26_10_06_joined))

Confirmed_State_3_26_10_06_joined_long <- Confirmed_State_3_26_10_06_joined %>% 
              pivot_longer(-c(Province_State),
                            names_to = "Date", values_to = "Confirmed")

ggplotly(
  ggplot(Confirmed_State_3_26_10_06_joined_long, aes(x = Confirmed,  y = Province_State))  + geom_bar(stat="identity",aes(color = Date)) +  labs(title="COVID-19 Confirmed Cases in US",
        x ="Number of Confirmed Cases", y = "State/Province in US")
 )
```

# US confirmed cases: 3/26/20 V. Today

* US Confirmed Cases: Seven Months Ago (3/26/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
daily_report3 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Country_Region == "US") %>% 
  filter (!Province_State %in% c("Alaska","Hawaii", "American Samoa",
                  "Puerto Rico","Northern Mariana Islands", 
                  "Virgin Islands", "Recovered", "Guam", "Grand Princess",
                  "District of Columbia", "Diamond Princess")) %>% 
  filter(Lat > 0)
ggplot(daily_report3, aes(x = Long, y = Lat, size = Confirmed/1000)) +
    borders("state", colour = "gold", fill = "azure1") +
    theme_minimal() +
    geom_point(shape = 21, color='hot pink', fill='pink', alpha = 0.5) +
    labs(title = 'COVID-19 Confirmed Cases in the US (3/26/20)', x = '', y = '',
        size="Cases (x1000))") +
    theme(legend.position = "right") +
    coord_fixed(ratio=1.5)
```

* US Confirmed Cases: Today (10/06/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
daily_report4 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/10-06-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Country_Region == "US") %>% 
  filter (!Province_State %in% c("Alaska","Hawaii", "American Samoa",
                  "Puerto Rico","Northern Mariana Islands", 
                  "Virgin Islands", "Recovered", "Guam", "Grand Princess",
                  "District of Columbia", "Diamond Princess")) %>% 
  filter(Lat > 0)
ggplot(daily_report4, aes(x = Long, y = Lat, size = Confirmed/1000)) +
    borders("state", colour = "gold", fill = "azure1") +
    theme_minimal() +
    geom_point(shape = 21, color='hot pink', fill='pink', alpha = 0.5) +
    labs(title = 'COVID-19 Confirmed Cases in the US (10/06/20)', x = '', y = '',
        size="Cases (x1000))") +
    theme(legend.position = "right") +
    coord_fixed(ratio=1.5)
```

# County Confirmed Cases: 3/26/20 V. Today

* County Confirmed Cases: Seven Months Ago (3/26/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
report_03_26_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  unite(Key, Admin2, Province_State, sep = ".") %>% 
  group_by(Key) %>% 
  summarize(Confirmed = sum(Confirmed)) %>% 
  mutate(Key = tolower(Key))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
US1<- map_data("state")
counties <- map_data("county") %>% 
  unite(Key, subregion, region, sep = ".", remove = FALSE)

# Join the 2 tibbles
state_join <- left_join(counties, report_03_26_2020, by = c("Key"))

# sum(is.na(state_join$Confirmed))
ggplot(data = US1, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  # Add data layer
  borders("state", colour = "black") +
  geom_polygon(data = state_join, aes(fill = Confirmed)) +
  scale_fill_gradientn(colors= 
                       wes_palette("GrandBudapest2", 100, type = "continuous"),
                       breaks = c(1, 10, 100, 1000, 10000, 100000),
                       trans = "log10", na.value = "White") +
  ggtitle("Number of Confirmed Cases by US County") +
  theme_minimal() 
```

* County Confirmed Cases: Today (10/06/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
report_10_06_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/10-06-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  unite(Key, Admin2, Province_State, sep = ".") %>% 
  group_by(Key) %>% 
  summarize(Confirmed = sum(Confirmed)) %>% 
  mutate(Key = tolower(Key))

# get and format the map data
US2 <- map_data("state")
counties <- map_data("county") %>% 
  unite(Key, subregion, region, sep = ".", remove = FALSE)

# Join the 2 tibbles
state_join <- left_join(counties, report_10_06_2020, by = c("Key"))

# sum(is.na(state_join$Confirmed))
ggplot(data = US2, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  
  # Add data layer
  borders("state", colour = "black") +
  geom_polygon(data = state_join, aes(fill = Confirmed)) +
   scale_fill_gradientn(colors= 
                       wes_palette("GrandBudapest2", 100, type = "continuous"),
                       breaks = c(1, 10, 100, 1000, 10000, 100000),
                       trans = "log10", na.value = "White") +
  ggtitle("Number of Confirmed Cases by US County") +
  theme_bw() 
```

# Interactive Graphs: Comparing the New York Confirmed Cases From Seven Months Ago (3/26/20) and Today (10/06/20)

* Confirmed Cases in New York (3/26/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
daily_report5 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Province_State == "New York") %>% 
  group_by(Admin2) %>% 
  summarize(Confirmed = sum(Confirmed)) %>% 
  mutate(Admin2 = tolower(Admin2))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
US3 <- map_data("state")
ny_us <- subset(US3, region == "new york")
counties <- map_data("county")
ny_county <- subset(counties, region == "new york")
state_join_ex4 <- left_join(ny_county, daily_report5, by = c("subregion" = "Admin2")) 
# plot state map
ggplotly(
  ggplot(data = ny_county, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
# Add data layer
  geom_polygon(data = state_join_ex4, aes(fill = Confirmed), color = "black") +
  ggtitle("COVID-19 Cases in NY (3/26/20)") +
 theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank()) +
  scale_fill_viridis(option="plasma")
)
```

* Confirmed Cases in New York (10/06/20)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
daily_report6 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/10-06-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Province_State == "New York") %>% 
  group_by(Admin2) %>% 
  summarize(Confirmed = sum(Confirmed)) %>% 
  mutate(Admin2 = tolower(Admin2))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
US4 <- map_data("state")
ny_us <- subset(US4, region == "new york")
counties <- map_data("county")
ny_county <- subset(counties, region == "new york")
state_join_ex4 <- left_join(ny_county, daily_report6, by = c("subregion" = "Admin2")) 

# plot state map
ggplotly(
  ggplot(data = ny_county, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
    
# Add data layer
  geom_polygon(data = state_join_ex4, aes(fill = Confirmed), color = "black") +
  ggtitle("COVID-19 Cases in NY (10/06/20)") +  
  theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank()) +
  scale_fill_viridis(option="plasma")
  
)
```

Application written in R [@RCoreTeam] using the Shiny framework [@Chang2015]. Data aquired from [@JohnsHopkinsUniversity].

# REFERENCES